251 Rescues

### 2024-10-09 code/process.Rmd
another attempt

for_pretty <- ready |>
  knitr::kable(format = "pipe") |>
  write_lines(here("data", "combined_data.md"))
```

>>>>

for_pretty <- ready |>

  select(
    target_lastauthor_year,
    type,
    short_cite,
    write_up_link,
    github_link,
   `pre-registration`,
    original_article_link=article_link,

    on_turk, 
    repeated_measure,
    N,
    raw_stat,
    same_direction,
    MCF_rep_score,
    TA_rep_score,
    replication_score,
    closeness,
    original_study_number=study_number,
    subfield,
    target_year,
    stanford_internal,
    open_data,
    open_materials,
    within_between,
    single_vignette,
  ) |> 
  knitr::kable(format = "pipe") |>
  write_lines(here("data", "combined_data.md")) 
```
